An Analysis of the SPDY Protocol as a Candidate for HTTP/2.0

### 2012-12-19 paper/paper.tex
Fin

This is contradictory to the results obtained by many other experimenters and
brings the accuracy of this experiment into question.  Clearly more work needs
to be done in order to find the cause of this discrepancy.  It seems likely that
the architecture of the server and client caused greater overheads with
variability than SPDY could have overcome and this hides the improvements made
with SPDY. It is also possible that there is an error in the implementation or
that some aspect of the design of the experiment is fundamentally flawed.  This
will need to be investigated before possibly going forward with this work.
% I don't want to remove this wholesale but I don't think it is relevant
% anywhere else in the paper. Maybe it fits somewhere?
% -Tom
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Evaluation}
% \label{sec:eval}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Once this data is collected the time difference will be found between each
% protocol's retrieval of each test page. The obvious next step will be to
% determine if SPDY actually made the pages load faster or not. In all likelihood,
% there will not be a constant speedup across all pages and so the next step of
% evaluation will be to see in which cases an improvement was found. This should
% give insight into how SPDY improves over the prior specification and help decide
% whether or not it is worth it for the actual upgrade of HTTP to take place.
%
% This success of this experiment will be based off of how many points of data can
% be acquired and how varying the conditions are for them.  Much of what will be
% included in the final report will be plots and tables of the data collected to
% allow the reader to decide for themselves.  This information will be useful to
% others and the measurement platform itself should be designed in such a way that
% future experiments can be run on it without too much effort to retool it.

@@

\section{List of Sites Used in Experiment}

>>>>

This is contradictory to the results obtained by many other experimenters and
brings the accuracy of this experiment into question.  Clearly more work needs
to be done in order to find the cause of this discrepancy.  It seems likely that
the architecture of the server and client caused greater overheads with
variability than SPDY could have overcome and this hides the improvements made
with SPDY. It is also possible that there is an error in the implementation or
that some aspect of the design of the experiment is fundamentally flawed.  This
will need to be investigated before possibly going forward with this work.

\section{Conclusion}
\label{sec:conlusion}
In this paper we have outlined the three candidates for HTTP/2.0: SPDY,
Speed+Mobility, and Network Friendly. We found potential for improvement from
SPDY based on our measurements of the web, but when we pushed further, no
improvement could be found.

% I don't want to remove this wholesale but I don't think it is relevant
% anywhere else in the paper. Maybe it fits somewhere?
% -Tom
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \section{Evaluation}
% \label{sec:eval}
% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Once this data is collected the time difference will be found between each
% protocol's retrieval of each test page. The obvious next step will be to
% determine if SPDY actually made the pages load faster or not. In all likelihood,
% there will not be a constant speedup across all pages and so the next step of
% evaluation will be to see in which cases an improvement was found. This should
% give insight into how SPDY improves over the prior specification and help decide
% whether or not it is worth it for the actual upgrade of HTTP to take place.
%
% This success of this experiment will be based off of how many points of data can
% be acquired and how varying the conditions are for them.  Much of what will be
% included in the final report will be plots and tables of the data collected to
% allow the reader to decide for themselves.  This information will be useful to
% others and the measurement platform itself should be designed in such a way that
% future experiments can be run on it without too much effort to retool it.

@@

\section{Sites Used in Experiment}
